Intentional release of native species undermines ecological stability

### 2022-10-05 rmd/supporting_info.Rmd
si

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
---

@@

```{r fig-2sp-w, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community. **(A)** Spearman's rank correlations between intentional release and community dynamics in a weak competition scenario ($\\bar{\\alpha}=$ ", min(list_param[[1]]$alpha) ,"). Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,"). Cells indicate 400 combinations of carrying capacity and intrinsic growth rate (20 values each). Colors are proportional to Spearman's rank correlations. Dots indicate parameter combinations that are used in the whole community simulation. **(B)** Examples of community dynamics with and without intentional release. Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins. Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations. Colors indicate release levels, and line types differ in carrying capacities.")}

source(here::here("code/figure_theory_2sp.R"))
knitr::include_graphics(here::here("output/figure_2sp_model_weak.pdf"))
```

@@

```{r fig-2sp-s, fig.width=9, fig.height=9, fig.cap = paste0("Theoretical predictions in a two-species community. **(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,"). Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,"). Cells indicate 400 combinations of carrying capacity and intrinsic growth rate (20 values each). Colors are proportional to Spearman's rank correlations. Dots indicate parameter combinations that are used in the whole community simulation. **(B)** Examples of community dynamics with and without intentional release. Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins. Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations. Colors indicate release levels, and line types differ in carrying capacities.")}

source(here::here("code/figure_theory_2sp.R"))
knitr::include_graphics(here::here("output/figure_2sp_model_strong.pdf"))
```

>>>>

---
output:
  bookdown::pdf_document2:
    fig_caption: true
    number_sections: true
    latex_engine: xelatex
    toc: true
    includes:
        before_body: title.tex
mainfont: "Times New Roman"
fontsize: 11pt
knit: (function(inputFile, encoding) {
        rmarkdown::render(inputFile,
                          encoding = encoding, 
                          output_dir = "document_output")
      })
header-includes:
  - \pagenumbering{gobble}
  - \usepackage{amsmath,fancyhdr, caption}
  - \captionsetup{width=1.3\linewidth, labelfont={bf}}
bibliography: reference.bib
csl: https://www.zotero.org/styles/pnas
nocite: |
  @duranteNoteMultiplicativeGamma2017, @myersMaximumReproductiveRate1999, @gotoEcologicalMorphologicalDivergence1975,@gotoLifeHistoryDistibution1981, @ministryofenvironmentofjapanThreatenedWildlifeJapan2014, @natsumedaEvaluationEcologicalFeatures2010, @fishbaseFishBaseHttpsWww
---

@@

```{r fig-2sp-w, fig.cap = paste0("Theoretical predictions in a two-species community. **(A)** Spearman's rank correlations between intentional release and community dynamics in a weak competition scenario ($\\bar{\\alpha}=$ ", min(list_param[[1]]$alpha) ,"). Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,"). Cells indicate 400 combinations of carrying capacity and intrinsic growth rate (20 values each). Colors are proportional to Spearman's rank correlations. Dots indicate parameter combinations that are used in the whole community simulation. Broken vertical lines denote the average value of $r_i$ (1.43) for salmonid species [@myersMaximumReproductiveRate1999]. **(B)** Examples of community dynamics with and without intentional release. Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins. Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations. Colors indicate release levels, and line types differ in carrying capacities.")}

source(here::here("code/si_figure_theory_2sp.R"))
knitr::include_graphics(here::here("output/figure_2sp_model_weak.pdf"))
```

@@

```{r fig-2sp-s, fig.cap = paste0("Theoretical predictions in a two-species community. **(A)** Spearman's rank correlations between intentional release and community dynamics in a strong competition scenario ($\\bar{\\alpha}=$ ", max(list_param[[1]]$alpha) ,"). Rows distinguish different summary statistics of community dynamics (top: CV, middle: mean, bottom: SD) while columns distinguish deterministic ($\\sigma_{\\varepsilon}=$ ", min(list_param[[1]]$sd_env) ,") and stochastic simulations ($\\sigma_{\\varepsilon}=$ ", max(list_param[[1]]$sd_env) ,"). Cells indicate 400 combinations of carrying capacity and intrinsic growth rate (20 values each). Colors are proportional to Spearman's rank correlations. Dots indicate parameter combinations that are used in the whole community simulation.  Broken vertical lines denote the average value of $r_i$ (1.43) for salmonid species [@myersMaximumReproductiveRate1999]. **(B)** Examples of community dynamics with and without intentional release. Community dynamics diverge at the broken vertical lines, the timestep at which intentional release begins. Rows distinguish intrinsic growth rates, while columns distinguish deterministic and stochastic simulations. Colors indicate release levels, and line types differ in carrying capacities.")}

source(here::here("code/si_figure_theory_2sp.R"))
knitr::include_graphics(here::here("output/figure_2sp_model_strong.pdf"))
```
